### 2008-12-18 talk/ecoop2009/benchmarks.tex
add tables showing the results. They need some restyling as they are very ugly.

Table XXX and figure XXX show the time spent to calculate the factorial of
various numbers, with and without the JIT.  Table XXX and figure XXX show the
same informations for the Fibonacci program.

Note that do get meaningful timings, we had to calculate the factorial and
Fibonacci of very high numbers.  This means that the results are incorrect due
to overflow, but since all the runnings overflows in the very same way, the
timings are still comparable. \anto{I think we should rephrase this sentence}.

As we can see, the code generated by the JIT is almost 500 times faster than
the non-jitted case, and it is only about 1.5 times slower than the same
algorithm written in C\#: the difference in speed it is probably due to both
the fact that the current CLI backend emits slightly non-optimal code and that
the underyling .NET JIT compiler is highly optimized to handle bytecode
generated by C\# compilers.

@@

Table XXX show the time spent to run the benchmark with various input
arguments. Again, we can see that the jitted code is up to 500 times faster
than the interpreted one.  Moreover, the code generated by the JIT is
\textbf{faster} than the equivalent C\# code.

>>>>

\anto{these tables are ugly}

\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.422  &  0.000  &  0.000  &      N/A  &    N/A \\
    $10^7$  &  30.984  &  0.453  &  0.047  &  0.031  &  661.000  &  1.500 \\
    $10^8$  &     N/A  &  0.859  &  0.453  &  0.359  &      N/A  &  1.261 \\
    $10^9$  &     N/A  &  4.844  &  4.641  &  3.438  &      N/A  &  1.350 \\

    \hline

  \end{tabular}
  \caption{Factorial benchmark}
  \label{tab:factorial}
\end{table}

\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.453  &  0.000  &  0.000  &       N/A  &  N/A   \\
    $10^7$  &  29.359  &  0.469  &  0.016  &  0.016  &  1879.962  &  0.999 \\
    $10^8$  &     N/A  &  0.688  &  0.250  &  0.234  &       N/A  &  1.067 \\
    $10^9$  &     N/A  &  2.953  &  2.500  &  2.453  &       N/A  &  1.019 \\

    \hline

  \end{tabular}
  \caption{Fibonacci benchmark}
  \label{tab:fibo}
\end{table}

Tables \ref{tab:factorial} and \ref{tab:fibo} show the time spent to calculate
the factorial and Fibonacci for various $n$.  As we can see, for small values
of $n$ the time spent running the JIT compiler is much higher than the time
spent to simply interpret the program.  This is an expected result, as till
now we only focused on optimizing the compiled code, not the compilation
process itself.

On the other hand, to get meaningful timings we had to use very high values of
$n$.  This means that the results are incorrect due to overflow, but since all
the runnings overflow in the very same way, the timings are still
comparable. \anto{I think we should rephrase this sentence}.  For $n$ greater
than $10^7$, we did not run the interpreted program as it would have took too
much time, without adding anything to the discussion.

As we can see, the code generated by the JIT can be up to ~1800 times faster
than the non-jitted case.  Moreover, it often runs at the same speed as the
equivalent program written in C\#, being only 1.5 slower in the worst case.

The difference in speed it is probably due to both the fact that the current
CLI backend emits slightly non-optimal code and that the underyling .NET JIT
compiler is highly optimized to handle bytecode generated by C\# compilers.

@@

\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.453  &  0.000  &  0.000  &      N/A  &  N/A   \\
    $10^7$  &  43.063  &  0.516  &  0.047  &  0.063  &  918.765  &  0.750 \\
    $10^8$  &     N/A  &  0.875  &  0.453  &  0.563  &      N/A  &  0.806 \\
    $10^9$  &     N/A  &  4.188  &  3.672  &  5.953  &      N/A  &  0.617 \\

    \hline

  \end{tabular}
  \caption{Accumulator benchmark}
  \label{tab:accumulator}
\end{table}

Table \ref{tab:accumulator} show the results for the benchmark.  Again, we can
see that the speedup of the JIT over the interpreter is comparable to the
other two benchmarks.  However, the really interesting part is the comparison
with the equivalent C\# code, as the code generated by the JIT is
\textbf{faster}.
